---
title: "Final Project"
author: "G5"
date: "11/18/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(psych)
#library(DataExplorer)
library(GGally)
library(corrplot)
library(DMwR)
library(caret)
library(VIM)
library(glmnet)
library(doParallel)
library(xgboost) 
library(mice)
library(data.table)
library(kableExtra)
#Please add any new required packages here:
```




```{r}
library(haven)
asthma.child <- read_sas("acbs_2016_child_public_llcp.sas7bdat")
View(asthma.child)
```

```{r}
#write.csv(asthma.child, "asthma_child.csv")
cn <- colnames(asthma.child)
write.csv(cn, "asthma_column_name.csv")
```

```{r}

```




## EXPLORATORY DATA ANALYSIS

```{r}

```

### CONSTRUCT THE RESPONSE VARIABLE
We first extract variables related to education, 
#### Selection of variables
```{r}
responses <- data.frame(
                        TCH.SIGN = asthma.child$TCH_SIGN, 
                        TCH.RESP = asthma.child$TCH_RESP,
                        TCH.MON = asthma.child$TCH_MON,
                        MGT.PLAN = asthma.child$MGT_PLAN,
                        MGT.CLAS = asthma.child$MGT_CLAS,
                        INHALERW = asthma.child$INHALERW,
                        MOD.ENV = asthma.child$MOD_ENV
                        )
head(responses)
```
Exploration
```{r}
responses.cat <- data.frame(apply(responses, 2, as.factor))
summary(responses.cat)
```




```{r}
# Initialize total within sum of squares error: wss
wss <- 0

# Look over 1 to 15 possible clusters
for (i in 1:16) {
  # Fit the model: km.out
  km.out <- kmeans(responses.cat, centers = i, nstart = 20, iter.max = 50)
  # Save the within cluster sum of squares
  wss[i] <- km.out$tot.withinss
}

# Produce a scree plot
plot(1:16, wss, type = "b", 
     xlab = "Number of Clusters", 
     ylab = "Within groups sum of squares")
```


```{r}
# Select number of clusters
k <- 9
```



```{r}
set.seed(2)
# Build model with k clusters: km.out
km.out <- kmeans(responses, centers = k, nstart = 20, iter.max = 50)

# View the resulting model
km.out$centers

```


##### add the point classification to the original data
```{r}
resp.asthma <- cbind(responses.cat, target = km.out$cluster)
head(resp.asthma)
write.csv(resp.asthma, "response_interpret.csv")
```


```{r}
resp.asthma$target <- as.factor(resp.asthma$target)
```




```{r}
summary(resp.asthma)
```

```{r}
plot(resp.asthma$target)
```
### INTERPRETATION OF ASTHMA RESPONSE CLUSTERING
#### WITH TCH.SIGN

```{r}
evar <- resp.asthma %>% 
  group_by(TCH.SIGN, target) %>%
  summarize(COUNT = n()) %>% 
  mutate(ETOTAL = sum(COUNT), PROPORTION = COUNT/ETOTAL)
evar
```

```{r}
tab1 <- evar %>% 
  group_by(TCH.SIGN) %>% 
  mutate(MAX.COUNT = max(COUNT)) %>%
  filter(COUNT==MAX.COUNT)
tab1
```

```{r}
ggplot(evar, aes(x = target, y = PROPORTION, group = TCH.SIGN, linetype = TCH.SIGN)) + geom_line()
```


#### WITH TCH.RESP
```{r}
evar <- resp.asthma %>% 
  group_by(TCH.RESP, target) %>%
  summarize(COUNT = n()) %>% 
  mutate(ETOTAL = sum(COUNT), PROPORTION = COUNT/ETOTAL)
evar
```



```{r}
tab2 <- evar %>% 
  group_by(TCH.RESP) %>% 
  mutate(MAX.COUNT = max(COUNT)) %>%
  filter(COUNT==MAX.COUNT)
tab2
```


```{r}
ggplot(evar, aes(x = target, y = PROPORTION, group = TCH.RESP, linetype = TCH.RESP)) + geom_line()
```



#### WITH TCH.MON

```{r}
evar <- resp.asthma %>% 
  group_by(TCH.MON, target) %>%
  summarize(COUNT = n()) %>% 
  mutate(ETOTAL = sum(COUNT), PROPORTION = COUNT/ETOTAL)
evar
```

```{r}
tab3 <- evar %>% 
  group_by(TCH.MON) %>% 
  mutate(MAX.COUNT = max(COUNT)) %>%
  filter(COUNT==MAX.COUNT)
tab3
```

```{r}
ggplot(evar, aes(x = target, y = PROPORTION, group = TCH.MON, linetype = TCH.MON)) + geom_line()
```


#### WITH MGT.PLAN

```{r}
evar <- resp.asthma %>% 
  group_by(MGT.PLAN, target) %>%
  summarize(COUNT = n()) %>% 
  mutate(ETOTAL = sum(COUNT), PROPORTION = COUNT/ETOTAL)
evar
```

```{r}
tab4 <- evar %>% 
  group_by(MGT.PLAN) %>% 
  mutate(MAX.COUNT = max(COUNT)) %>%
  filter(COUNT==MAX.COUNT)
tab4
```

```{r}
ggplot(evar, aes(x = target, y = PROPORTION, group = MGT.PLAN, linetype = MGT.PLAN)) + geom_line()
```


#### WITH MGT.CLAS

```{r}
evar <- resp.asthma %>% 
  group_by(MGT.CLAS, target) %>%
  summarize(COUNT = n()) %>% 
  mutate(ETOTAL = sum(COUNT), PROPORTION = COUNT/ETOTAL)
evar
```

```{r}
tab5 <- evar %>% 
  group_by(MGT.CLAS) %>% 
  mutate(MAX.COUNT = max(COUNT)) %>%
  filter(COUNT==MAX.COUNT)
tab5
```

```{r}
ggplot(evar, aes(x = target, y = PROPORTION, group = MGT.CLAS, linetype = MGT.CLAS)) + geom_line()
```


#### WITH INHALERW 

```{r}
evar <- resp.asthma %>% 
  group_by(INHALERW, target) %>%
  summarize(COUNT = n()) %>% 
  mutate(ETOTAL = sum(COUNT), PROPORTION = COUNT/ETOTAL)
evar
```

```{r}
tab6 <- evar %>% 
  group_by(INHALERW ) %>% 
  mutate(MAX.COUNT = max(COUNT)) %>%
  filter(COUNT==MAX.COUNT)
tab6
```

```{r}
ggplot(evar, aes(x = target, y = PROPORTION, group = INHALERW , linetype = INHALERW)) + geom_line()
```


#### WITH  MOD.ENV

```{r}
evar <- resp.asthma %>% 
  group_by( MOD.ENV, target) %>%
  summarize(COUNT = n()) %>% 
  mutate(ETOTAL = sum(COUNT), PROPORTION = COUNT/ETOTAL)
evar
```

```{r}
tab7 <- evar %>% 
  group_by( MOD.ENV) %>% 
  mutate(MAX.COUNT = max(COUNT)) %>%
  filter(COUNT==MAX.COUNT)
tab7
```

```{r}
ggplot(evar, aes(x = target, y = PROPORTION, group =  MOD.ENV, linetype =  MOD.ENV)) + geom_line()
```


#### Recapitulating the asthma self-management interpretation
```{r}
trecap <- data.frame(RESPONSE = c("1=YES", "2=NO", "7=DONT KNOW", "9=REFUSED"),
                     TCH.SIGN = tab1$target,
                     TCH.RESP = tab2$target,
                     TCH.MON = tab3$target,
                     MGT.PLAN = tab4$target,
                     MGT.CLAS = tab5$target,
                     INHALERW = tab6$target[-c(3)],
                     MOD.ENV = tab7$target
                     )
trecap
```



ASTHNOW Have you ever been told by a doctor or other health professional that you have
asthma?

TCH_SIGN  Has a doctor or other health professional ever taught you...
a. How to recognize early signs or symptoms of an asthma episode?

TCH_RESP Has a doctor or other health professional ever taught you...
b. What to do during an asthma episode or attack?

TCH_MON A peak flow meter is a hand held device that measures how quickly you can blow air
out of your lungs. Has a doctor or other health professional ever taught you…
c. How to use a peak flow meter to adjust your daily medications?

MGT_PLAN An asthma action plan, or asthma management plan, is a form with instructions
about when to change the amount or type of medicine, when to call the doctorfor
advice, and when to go to the emergency room.
Has a doctor or other health professional EVER given you an asthma action plan?

MGT_CLAS Have you ever taken a course or class on how to manage your asthma?

INHALERH (8.3) Did a doctor or other health professional show you how to use the inhaler?

INHALERW (8.4) Did a doctor or other health professional watch you use the inhaler?

Responses types
(1) YES
(2) NO
(7) DON’T KNOW
(9) REFUSED

Predictors

MISS_DAY = "NUMBER OF MISSED DAYS"
MOD_ENV = "EVER ADVISED CHANGE THINGS IN YOUR HOME"
AGEDX = "AGE AT ASTHMA DIAGNOSIS"
AGEG_F6_M = "MODIFIED SIX AGE GROUPS USED IN ASTHMA child POST-STRATIFICATION"
AIRCLEANER = "AIR CLEANER USED"
ASMDCOST = "COST BARRIER: PRIMARY CARE DOCTOR"
ASRXCOST = "COST BARRIER: MEDICATION"
ASSPCOST = "COST BARRIER: SPECIALIST"
CATTMPTS_F = "DISPOSITION CODES FOR CALL ATTEMPTS 1 THROUGH 20 ..."
EMP_STAT = "CURRENT EMPLOYMENT STATUS"
EPIS_12M = "ASTHMA EPISODE OR ATTACK"
EPIS_TP = "NUMBER OF EPISODES / ATTACKS"
ER_TIMES = "NUMBER OF EMERGENCY ROOM VISITS"
ER_VISIT = "EMERGENCY ROOM VISIT"
EVER_ASTH = "EVER HAVE ASTHMA INCONSISTENT WITH BRFSS"
#FLAG1 = "FLAG FOR AGE, AGEDX, INCIDNT INCONSISTENCY"
HOSPPLAN = "HOSPITAL FOLLOW-UP"
HOSPTIME = "NUMBER OF HOSPITAL VISITS"
HOSP_VST = "HOSPITAL VISIT"
QSTLANG_F = "LANGUAGE IDENTIFIER"
SCR_MED3 = "HAVE ALL THE MEDICATIONS"
#SEQNO = "ANNUAL SEQUENCE NUMBER"
UNEMP_R = "REASON NOT NOW EMPLOYED"
URG_TIME = "NUMBER OF URGENT VISITS"
WORKENV5 = "ASTHMA AGGRAVATED BY CURRENT JOB"
WORKENV6 = "ASTHMA CAUSED BY CURRENT JOB"
WORKENV7 = "ASTHMA AGGRAVATED BY PREVIOUS JOB"
WORKENV8 = "ASTHMA CAUSED BY PREVIOUS JOB"
WORKQUIT1 = "EVER CHANGE OR QUIT A JOB"
WORKSEN3 = "DOCTOR DIAGNOSED WORK ASTHMA"
WORKSEN4 = "SELF-IDENTIFIED WORK ASTHMA"
WORKTALK = "DOCTOR DISCUSSED WORK ASTHMA"
INS1 = "INSURANCE"
INS2 = "INSURANCE OR COVERAGE GAP"
LANDWT_F = "FINAL child ASTHMA CALL-BACK WEIGHT"
LASTSYMP = "LAST HAD ANY SYMPTOMS OF ASTHMA"
LAST_MD = "LAST TALKED TO A DOCTOR"
LAST_MED = "LAST TOOK ASTHMA MEDICATION"
LLCPWT_F  = "child ASTHMA FINAL WEIGHT"
RACEG_F = "RACE COLLAPSED TO 1 GROUP FOR ASTHMA CALL-BACK"
REGION_F = "REGIONS COLLAPSED TO 1 REGION FOR ASTHMA CALL-BACK.
COMPASTH = "TYPICAL ATTACK"



### Constructing the data frame by selecting predictors

```{r}
asthma.mgt.child1 <- data.frame(TARGET = resp.asthma$target,
                                SEX = asthma.child$SEX,
                                AGEG6 = asthma.child[,"_AGE_G"],
                                RACE = asthma.child[, "_RACEGR3"],
                                EDUCAL = asthma.child$EDUCA,
                                INCOMEL = asthma.child$INCOME2,
                                RFBMIS = asthma.child[, "_RFBMI5"],
                                SMOKE100 = asthma.child$SMOKE100,
                                SYMP.30D = asthma.child$SYMP_30D,
                                DUR.30D = asthma.child$DUR_30D,
                                ASLEEP30 = asthma.child$ASLEEP30,
                                INCINDT = asthma.child$INCIDNT,
                                LAST.MD = asthma.child$LAST_MD,
                                LAST.MED = asthma.child$LAST_MED,
                                LAST.SYMP = asthma.child$LASTSYMP,
                                EPIS.12M = asthma.child$EPIS_12M,
                                EPIS.TP = asthma.child$EPIS_TP,
                                DUR.ASTH = asthma.child$DUR_ASTH,
                                COMPASTH = asthma.child$COMPASTH,
                                INS1 = asthma.child$INS1,
                                INS2 = asthma.child$INS2,
                                ER.TIMES = asthma.child$ER_TIMES,
                                ER.VISIT = asthma.child$ER_VISIT,
                                URG.TIMES = asthma.child$URG_TIME,
                                HOSP.VST = asthma.child$HOSP_VST,
                                HOSPTIME = asthma.child$HOSPTIME,
                                HOSPPLAN = asthma.child$HOSPPLAN,
                                ASMDCOST = asthma.child$ASMDCOST,
                                ASRXCOST = asthma.child$ASRXCOST,
                                ASSPCOST = asthma.child$ASSPCOST
                                )
```






```{r}
head(asthma.mgt.child1)
```



Structure
```{r}
str(asthma.mgt.child1)
attach(asthma.mgt.child1)
```


Summary
```{r}
summary(asthma.mgt.child1)
```



### Univariate 

### EXPLORE THE DATA
Histogram of the target variable
```{r}
ggplot(data=asthma.mgt.child1, aes(x=TARGET)) + geom_bar()
```
### We look over the predictors distribution
```{r}
par(mfrow = c(2,4))
for (x in colnames(asthma.mgt.child1)[-1]){
  boxplot(asthma.mgt.child1[,x],main=x)
}
```

#### Histograms       
Histograms tell us how the data is distributed in the dataset (numeric fields).    

```{r, message = FALSE, warning = FALSE, echo = F}
multi.hist(asthma.mgt.child1[2:9])
multi.hist(asthma.mgt.child1[10:17])
multi.hist(asthma.mgt.child1[18:25])
multi.hist(asthma.mgt.child1[25:30])
```


#### The correlations betweeen predictors

```{r}
cor_asthma.child <- cor(asthma.mgt.child1[,-1], use = "na.or.complete")
corrplot(cor_asthma.child, order = 'hclust', type = 'lower')
```

```{r}
# cor(asthma.mgt.child1[,-1], use = "na.or.complete")
# write.csv(cor(asthma.mgt.child1[,-1], use = "na.or.complete"), "predictors_cor.csv")
```
We are removing the predictor X_BMISCAT because it has to much missing values 
There are highly correlated predictors. We are going to remove some of them.
```{r}
# asthma.mgt.child2 <- select(asthma.mgt.child1, -EPIS.TP, -HOSPPLAN, -ASSPCOST, -ASMDCOST, -ER.VISIT, DUR.ASTH)
# colnames(asthma.mgt.child2)
```




### Divers Correlations with the response variable


```{r}
ggplot(asthma.mgt.child1, aes(x=EDUCAL, y=COMPASTH, color = TARGET)) + geom_point(position = position_jitter(), alpha=.3) + facet_grid(rows = vars(SEX), cols = vars(X_RACEGR3))
```

```{r}
ggplot(asthma.mgt.child1, aes(x=X_AGE_G, y=LAST.SYMP, color = TARGET)) +
  geom_point() +
  facet_grid(rows = vars(SEX), cols = vars(X_RACEGR3))
```

Relationship between the target variable and the predictor
```{r}
egt <- summarize(group_by(asthma.mgt.child1, EDUCAL, TARGET), COUNT = n())
egt <- mutate(egt, ETOTAL = sum(COUNT), PROPORTION = COUNT/ETOTAL)
ggplot(egt, aes(x=EDUCAL, y=PROPORTION, group = TARGET, linetype = TARGET)) + geom_line()
```

Relationship between the target variable and the predictor
```{r}
egt <- summarize(group_by(asthma.mgt.child1, X_RACEGR3, TARGET), COUNT = n())
egt <- mutate(egt, ETOTAL = sum(COUNT), PROPORTION = COUNT/ETOTAL)
ggplot(egt, aes(x=X_RACEGR3, y=PROPORTION, group = TARGET, linetype = TARGET)) + geom_line()
```





### PREPARE THE DATA FOR MODELISATION

#### We remove the rows with missing values.
Here were are going to drop missing data because they are only 12  over 13,922 rows.
We also transform all predictors to categorical.
```{r}
asthma.mgt.child2 <- drop_na(asthma.mgt.child2)
asthma.mgt.child2 <- data.frame(apply(asthma.mgt.child2, 2, as.factor))
summary(asthma.mgt.child2)
```


### BUILDS MODELS


### SELECT MODELS


### APPLY THE MODELS TO A DIFFERENT DATASET






